Doublets figure

### 2020-05-04 main_figures/doublets.Rmd
reduced width

```{r figure1, fig.height=6, fig.width=8}
p1m <- plot_grid(p1, p2, p3, nrow=1, rel_widths = c(9,10,10))
pdf("doublets.pdf", width=8, height=6)
plot_grid(p1m, pt, p4, rel_heights=c(3.5,2,2), labels = LETTERS[1:3], ncol = 1, hjust=0, scale=0.95)
dev.off()
plot_grid(p1m, pt, p4, rel_heights=c(3.5,2,2), labels = LETTERS[1:3], ncol = 1, hjust=0)
```

>>>>

```{r figure1, fig.height=6, fig.width=7}
p1m <- plot_grid(p1, p2, p3, nrow=1, rel_widths = c(9,10,10))
pdf("doublets.pdf", width=7, height=6)
plot_grid(p1m, pt, p4, rel_heights=c(3.5,2,2), labels = LETTERS[1:3], ncol = 1, hjust=0, scale=0.95)
dev.off()
plot_grid(p1m, pt, p4, rel_heights=c(3.5,2,2), labels = LETTERS[1:3], ncol = 1, hjust=0)
```
